Analysis paper

### 2021-06-25 analysis/analysis.Rmd
update plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)

@@

   scores_target_forecastdate[horizon == i & target_type == "case"] %>%
    scores_over_time_plot_components() + 
    scale_color_manual(values = colcases) + 
    labs(y = "WIS rel. to baseline", x = "")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)

@@

# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
#   scores_over_time_plot_components() + 
#   scale_color_manual(values = colcases) + 
#   labs(y = "WIS rel. to baseline", x = "")
